---
title: "brt-analysis-step-2"
format: html
editor: visual
---

Step 2 of the boosted regression tree analysis, this analysis looks at the implications of including coniferous forest cover to the data.

---
title: "brt-analysis-step-1"
format: html
editor: visual
date: 2023-06-12
---

# Analysis setup

### required packages

```{r}
library(caret)
library(gbm)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tidymodels)
```

### read in fire data

```{r}
data_tlm <- read.csv("~/Work/PhD/MoistureAvailability//data/bs-moisture-lags-data-v0.csv")

#clean names
names(data_tlm) <- data_tlm %>% names () %>%  str_replace_all(.,"^X", "")
```

### read in covariates

```{r}
#covariates
covariates <- read.csv("~/Google Drive/My Drive/boreal-fires-forest-area-calc/nwo-forest-cover-v0.csv")
#select covariates of interest
covariates <- select(covariates, c("raster_id", "coniferPercent", "forestPercent"))

#fwi
fwi.dur <- read.csv("~/Desktop/OneDrive - University of Toronto/Data/ontario-fire-disturbance-data/climate-data/fwi-90th-fire-duration.csv")
#add rbr to the end of fire id
fwi.dur2<- fwi.dur %>% 
  mutate(raster_id = paste0(Fire_ID, "_rbr")) %>% 
  select(-c(Fire_ID))

```


### clean data

```{r}
#join covariates to climate data and remove id
data_tlm <- data_tlm %>% 
semi_join(covariates, by = "raster_id") %>% 
  left_join(fwi.dur2, by = "raster_id") %>% 
  left_join(covariates, by = "raster_id") %>% select(-c(1))

data_tlm <- data_tlm %>% drop_na()

#select only fires with >= 50 confiferous forest cover
data_tlm <- data_tlm %>% 
  select(-c(coniferPercent, forestPercent))
# Remove first column
data_tlm_clean <- data_tlm %>%  
  select(-c(1, X))

#split data set into Extreme only and Median only

med_tlm <- data_tlm_clean %>% 
  select(-c(2))

ext_tlm <- data_tlm_clean %>% 
  select(-c(1))
```

### create testing and training data

```{r}
### Split data into test vs. training ###

# Extreme
set.seed(429)#set seed for reproducibility


ext_split <- initial_split(ext_tlm, prop = 5/8)
ext_train <- training(ext_split)
ext_test  <- testing(ext_split)

# Median
set.seed(429)##set seed for reproducibility


med_split <- initial_split(med_tlm, prop = 5/8)
med_train <- training(med_split)
med_test  <- testing(med_split)


```

First thing is to set up the defaults of the model. These are the metrics that will be used for both trees we use RMSE. We also set up the control grid for tuning. Additionally, we set up the cross-validation process for our training model using 10-fold Cross-Validation

# Burn Severity Extremes

### set up defaults

```{r}
mset <- metric_set(rmse) 
control <- control_grid(save_workflow = TRUE,
                        save_pred = TRUE,
                        extract = extract_model) # grid for tuning


set.seed(429) #set seed for reproducibility

ext_folds <- vfold_cv(ext_train, v = 10)
```




###  build up the recipe, or our model fit

```{r}
ext_fit = recipe(RBR_quant ~., data = ext_train) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_corr(all_numeric_predictors(), threshold = .8) %>% prep
```



### Now to specify the model

```{r}
ext_tune_spec = 
  boost_tree(trees =  tune(),
             tree_depth = tune(),
             learn_rate = tune(),
             min_n = tune(),
             sample_size = tune(),
             loss_reduction = tune(),
             mtry = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("xgboost", counts = FALSE)

```


### set workflow 

```{r}
ext_wf <- workflow() %>%
  add_recipe(ext_fit) %>% 
  add_model(ext_tune_spec)
```


### Run model with tuning grid 

```{r}
#Use 10-fold cross-validation to evaluate the model with different hyperparameters

#get best model from step 1
readRDS("~/Desktop/OneDrive - University of Toronto/Projects/burn-severity-time-lagged-moisture/models/ext-model-final-259-clim-only.rds")

set.seed(429) #set seed for reproducibility

ext_tune<-  ext_wf %>% 
  tune_grid(resample = ext_folds,
            metrics = mset,
            control = control,
            grid = crossing( 
              trees = c(1000, 2000),
              tree_depth = c(6),
              learn_rate = c(0.005, 0.0025, 0.01),
              min_n = c(2,10,15),
              sample_size = c(0.6),
              loss_reduction = c(5, 8),
              mtry = c(0.5)))
```



### Check out accuracy on testing dataset to see if we overfitted.
```{r}
set.seed(429)
ext_fit_train <- ext_wf %>% 
  finalize_workflow(select_best(ext_tune)) %>% fit(ext_train)
ext_fit_test <- ext_wf %>% 
  finalize_workflow(select_best(ext_tune)) %>% fit(ext_test)


ext_best_params <- ext_tune %>%
  tune::select_best("rmse")

ext_model_final <- ext_tune_spec %>% 
  finalize_model(ext_best_params)
ext_model_final
saveRDS(ext_model_final, "~/Desktop/OneDrive - University of Toronto/Projects/burn-severity-time-lagged-moisture/models/ext-model-final-259-clim-fwi.rds")
# get accuracy
train_processed <- bake(ext_fit,  new_data = ext_train)
train_prediction <- ext_model_final %>%
  # fit the model on all the training data
  fit(
    formula = RBR_quant ~ ., 
    data    = train_processed
  ) %>%
  # predict the sale prices for the training data
  predict(new_data = train_processed) %>%
  bind_cols(ext_train)
ext_score_train <- 
  train_prediction %>%
  yardstick::metrics(RBR_quant, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))

test_processed <- bake(ext_fit,  new_data = ext_test)
test_prediction <- ext_model_final %>%
  # fit the model on all the training data
  fit(
    formula = RBR_quant ~ ., 
    data    = test_processed
  ) %>%
  # predict the sale prices for the training data
  predict(new_data = test_processed) %>%
  bind_cols(ext_test)
ext_score_test <- 
  test_prediction %>%
  yardstick::metrics(RBR_quant, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
ext_score_test
ext_score_train

write.csv(ext_score_test, "~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/ext-score-test-259-clim-fwi.csv")

write.csv(ext_score_train, "~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/ext-score-train-259-clim-fwi.csv")
```


### Extract and visualize variable importance

```{r}
ext_imp <- xgboost::xgb.importance(model = extract_fit_engine(ext_fit_test))

ext_imp %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>% 
  dplyr::slice_max(Gain, n = 10) %>% 
  ggplot(aes(Gain, Feature, fill = Feature)) +
  geom_col() + scale_fill_viridis_d()+ theme_bw()  +
  theme(legend.position="none") + 
  labs(title = "Burn Severity Extremes", y = "Predictor") +
  theme(plot.title = element_text(hjust = 0.5))

# save variable importance as csv
write.csv(ext_imp, "~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/brt-extremes-imp-259-clim-fwi.csv")
```

# Median wildfire Burn Severity 

### set up defaults
```{r}
mset <- metric_set(rmse) # metric is accuracy
control <- control_grid(save_workflow = TRUE,
                        save_pred = TRUE,
                        extract = extract_model) # grid for tuning


#10 fold cross val
cvFolds_med <- med_train %>% vfold_cv(10)
```



### build recipe
```{r}
med_rec = recipe(RBR_median ~., data = med_train) %>% 
  step_normalize(all_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_corr(all_numeric_predictors(), threshold = .8) %>% prep()
```

### specify BRT model

```{r}
med_tune_spec = 
  boost_tree(trees =tune(),
             tree_depth = tune(),
             learn_rate = tune(),
             min_n = tune(),
             sample_size = tune(),
             loss_reduction = tune(),
             mtry = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("xgboost", counts = FALSE)


```


### set workflow

```{r}
med_wf <- workflow() %>%
  add_recipe(med_rec) %>% 
  add_model(med_tune_spec)
```


### use CV to evaluate the model with different hyperparameters
```{r}
set.seed(429)
med_tune<-  med_wf %>% 
  tune_grid(resamples = cvFolds_med,
            metrics = mset,
            control = control,
            grid = crossing( 
              trees = c(1000, 2000),
              tree_depth = c(6),
              learn_rate = c(0.01, 0.005),
              sample_size = c(0.6, 0.7),
              loss_reduction = c(5, 8, 15),
              min_n = c(1),
              mtry = c(0.5)))
```



### Use best tuning specifications to fit model to training data.
```{r}
set.seed(429)
med_fit <- med_wf %>% 
  finalize_workflow(select_best(med_tune)) %>% 
  fit(med_train)
```


### Check out accuracy on testing dataset to see if we overfitted.
```{r}
set.seed(429)
med_fit_train <- med_wf %>% 
  finalize_workflow(select_best(med_tune)) %>% fit(med_train)
med_fit_test <- med_wf %>% 
  finalize_workflow(select_best(med_tune)) %>% fit(med_test)


med_best_params <- med_tune %>%
  tune::select_best("rmse")

med_model_final <- med_tune_spec %>% 
  finalize_model(med_best_params)

# get accuracy
train_processed <- bake(med_rec,  new_data = med_train)
train_prediction <- med_model_final %>%
  # fit the model on all the training data
  fit(
    formula = RBR_median ~ ., 
    data    = train_processed
  ) %>%
  # predict the sale prices for the training data
  predict(new_data = train_processed) %>%
  bind_cols(med_train)
med_score_train <- 
  train_prediction %>%
  yardstick::metrics(RBR_median, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))

test_processed <- bake(med_rec,  new_data = med_test)
test_prediction <- med_model_final %>%
  # fit the model on all the training data
  fit(
    formula = RBR_median ~ ., 
    data    = test_processed
  ) %>%
  # predict the sale prices for the training data
  predict(new_data = test_processed) %>%
  bind_cols(med_test)
med_score_test <- 
  test_prediction %>%
  yardstick::metrics(RBR_median, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
med_score_test
med_score_train
write.csv(med_score_test, "~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/med-score-test-259-clim-fwi.csv")

write.csv(med_score_train, "~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/med-score-train-259-clim-fwi.csv")
```

### Extract and plot variable importance

```{r}
med_imp <- xgboost::xgb.importance(model = extract_fit_engine(med_fit_test))

med_imp %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>% 
  dplyr::slice_max(Gain, n = 10) %>% 
  ggplot(aes(Gain, Feature, fill = Feature)) +
  geom_col() + scale_fill_viridis_d()+ theme_bw()  +
  theme(legend.position="none") + 
  labs(title = "Median Burn Severity within AOU", y = "Predictor") +
  theme(plot.title = element_text(hjust = 0.5)) 

# save variable importance as csv
write.csv(med_imp, "~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/brt-med-imp-259-clim-fwi.csv")
```

# Plot model results
```{r}
med_imp <- read.csv("~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/brt-med-imp-259-clim-fwi.csv")
ext_imp <- read.csv("~/Desktop/OneDrive - University of Toronto/Data/moisture-data-chap1/brt-extremes-imp-259-clim-fwi.csv")

# figure S1 full model relative importance -----------
# Median
library(tidyverse)
library(gridExtra)
library(lubridate)
library(ggplot2)
library(EnvStats)
library(ggpubr)
library(ggpattern)
library(viridis)
library(DALEXtra)

full.imp.im.plot= med_imp %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>% 
    mutate(Feature = fct_rev(Feature)) %>% 
  mutate(Predictor_Class = case_when(
    grepl("C", Feature) ~ "Climate Moisture Index",
    grepl("R", Feature) ~ "Relative Humidity",

    grepl("isi_90", Feature) ~ "Fire Weather Indices",
    grepl("dmc_90", Feature )~ "Fire Weather Indices",
    grepl("dc_90", Feature )~ "Fire Weather Indices",
    grepl("fwi_90", Feature )~ "Fire Weather Indices",
    grepl("bui_90", Feature )~ "Fire Weather Indices",
    grepl("ffmc_90", Feature )~ "Fire Weather Indices",

    
  )) %>% 
  mutate(Temporal_Dynamics = case_when(
    grepl("yCsum", Feature) ~ "Yearly",
    grepl("yRmean", Feature) ~ "Yearly",
    grepl("mCsum", Feature) ~ "Monthly",
    grepl("mRmean", Feature) ~ "Monthly",
    grepl('m', Feature) ~ "Monthly",
    grepl('y', Feature) ~ "Yearly",
    grepl("isi_90", Feature) ~ "Fire Duration",
    grepl("dmc_90", Feature )~ "Fire Duration",
    grepl("dc_90", Feature )~ "Fire Duration",
    grepl("fwi_90", Feature )~ "Fire Duration",
    grepl("bui_90", Feature )~ "Fire Duration",
    grepl("ffmc_90", Feature )~ "Fire Duration",
  )) %>% 
  ggplot(aes(Gain, Feature, fill = Predictor_Class, width = .8), color = "black") +
  geom_col_pattern(
    aes(pattern = Temporal_Dynamics),
    colour = "black",
    pattern_fill = "black",
    pattern_angle = 45,
    pattern_density = 0.05,
    pattern_spacing = 0.03,
    position = position_dodge2(preserve = 'single')) +
  coord_flip() +
  scale_pattern_manual(values = c("wave", "none", "stripe" ), "Temporal Dynamics",
                       guide = guide_legend(override.aes = list(fill = "white"))) +
  theme(text = element_text(size = 8)) +
  
  scale_fill_manual(values = c ("purple","firebrick1", "coral"), "Predictor Class", 
                    guide = guide_legend(override.aes = list(pattern = "none")))+
  theme_bw()+
  labs(title = "Median Burn Severity",  x = "Relative Influence (%)", y = "Predictors") +
  scale_x_continuous(labels = scales::percent)+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


full.imp.im.plot
```

### Extremes
```{r}

full.imp.iq.plot= ext_imp %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>% 
  mutate(Feature = fct_rev(Feature)) %>% 
  mutate(Predictor_Class = case_when(
    grepl("C", Feature) ~ "Climate Moisture Index",
    grepl("R", Feature) ~ "Relative Humidity",

    grepl("isi_90", Feature) ~ "Fire Weather Indices",
    grepl("dmc_90", Feature )~ "Fire Weather Indices",
    grepl("dc_90", Feature )~ "Fire Weather Indices",
    grepl("fwi_90", Feature )~ "Fire Weather Indices",
    grepl("bui_90", Feature )~ "Fire Weather Indices",
    grepl("ffmc_90", Feature )~ "Fire Weather Indices",

    
  )) %>% 
  mutate(Temporal_Dynamics = case_when(
    grepl("yCsum", Feature) ~ "Yearly",
    grepl("yRmean", Feature) ~ "Yearly",
    grepl("mCsum", Feature) ~ "Monthly",
    grepl("mRmean", Feature) ~ "Monthly",
    grepl('m', Feature) ~ "Monthly",
    grepl('y', Feature) ~ "Yearly",
    grepl("isi_90", Feature) ~ "Fire Duration",
    grepl("dmc_90", Feature )~ "Fire Duration",
    grepl("dc_90", Feature )~ "Fire Duration",
    grepl("fwi_90", Feature )~ "Fire Duration",
    grepl("bui_90", Feature )~ "Fire Duration",
    grepl("ffmc_90", Feature )~ "Fire Duration",
  )) %>% 
  ggplot(aes(Gain, as.factor(Feature), fill = Predictor_Class, width = .8), color = "black") + 
  geom_col_pattern(
    aes(pattern = Temporal_Dynamics),
    colour = "black",
    pattern_fill = "black",
    pattern_angle = 45,
    pattern_density = 0.05,
    pattern_spacing = 0.03,
    position = position_dodge2(preserve = 'single')) +
  scale_pattern_manual(values = c("wave", "none", "stripe" ), "Temporal Dynamics",
                       guide = guide_legend(override.aes = list(fill = "white"))) +
  theme(text = element_text(size = 8))+
  scale_fill_manual(values = c("purple","firebrick1", "coral"), "Predictor Class", 
                    guide = guide_legend(override.aes = list(pattern = "none")))+
  theme_bw()+
  labs(title = "Burn Severity Extremes",  x = "Relative Influence (%)", y = "Predictors") +
  scale_x_continuous(labels = scales::percent)+
  coord_flip()+ 
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

full.imp.iq.plot
```


```{r}
# arrange plots
ggarrange(full.imp.im.plot, full.imp.iq.plot, 
          labels = c("A", "B"),
          ncol = 1, nrow = 2, widths = c(1,1),
          heights = c(5,5),
          common.legend = TRUE, legend="bottom")

```



